Predictive Regressions with Persistent Regressors

### 2019-09-07 paper.tex
cleaned up tables

\subsection{A pretest}
From equation ... it's easy to see that if $\delta = 0$ the nuisance term $\tau_{c} / \kappa_{c}$ vanishes and the t-statistic collapses to the standard normal  random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. Phillips (1987) shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

@@

To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates of the true null for right-tailed tests of predictability at $\alpha$=0.05 (10,000 Monte Carlo samples).}
\label{tab:cy}
\centering
\begin{tabular}{rrrrrrrr}
 \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4160 & 0.0826 & 0.0483 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2916 & 0.0837 & 0.0515 \\ 
  3 & 50 & -2 & 0.961 & -0.95 & 0.2714 & 0.0868 & 0.0482 \\ 
  4 & 50 & -2 & 0.961 & -0.75 & 0.2079 & 0.0881 & 0.0532 \\ 
  5 & 50 & -20 & 0.608 & -0.95 & 0.0977 & 0.1206 & 0.0515 \\ 
  6 & 50 & -20 & 0.608 & -0.75 & 0.0840 & 0.1078 & 0.0484 \\ 
  7 & 100 & 0 & 1.000 & -0.95 & 0.4217 & 0.0616 & 0.0480 \\ 
  8 & 100 & 0 & 1.000 & -0.75 & 0.2930 & 0.0616 & 0.0497 \\ 
  9 & 100 & -2 & 0.980 & -0.95 & 0.2698 & 0.0587 & 0.0505 \\ 
  10 & 100 & -2 & 0.980 & -0.75 & 0.2104 & 0.0588 & 0.0489 \\ 
  11 & 100 & -20 & 0.802 & -0.95 & 0.1063 & 0.0622 & 0.0471 \\ 
  12 & 100 & -20 & 0.802 & -0.75 & 0.0874 & 0.0514 & 0.0500 \\ 
  13 & 250 & 0 & 1.000 & -0.95 & 0.4259 & 0.0476 & 0.0483 \\ 
  14 & 250 & 0 & 1.000 & -0.75 & 0.2970 & 0.0506 & 0.0536 \\ 
  15 & 250 & -2 & 0.992 & -0.95 & 0.2866 & 0.0507 & 0.0481 \\ 
  16 & 250 & -2 & 0.992 & -0.75 & 0.2092 & 0.0466 & 0.0492 \\ 
  17 & 250 & -20 & 0.920 & -0.95 & 0.1080 & 0.0406 & 0.0517 \\ 
  18 & 250 & -20 & 0.920 & -0.75 & 0.0944 & 0.0369 & 0.0501 \\ 
   \hline
\end{tabular}
\end{table}

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rate close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates  of the true null for right-tailed and two-tailed tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively (10,000 Monte Carlo samples).}
\centering
\label{tab:cy_changed}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
   \hline
\end{tabular}
\end{table}

As argued by Phillips (2014), the Q-test as derived in section (3) is asymptotically invalid when the largest autoregressive root of the regressor is not local to unity. In the following I will demonstrate the finite sample behavior as $\rho$ diverges from unity. Again 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. 
\begin{table}[h!]
\caption{Finite-sample rejection rates of the true null for right-tailed and two-tailed tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root (10,000 Monte Carlo samples). }
\label{tab:non-local}
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4147 & 0.0946 & 0.0480 & 0.0957 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2810 & 0.0838 & 0.0475 & 0.0870 \\ 
  3 & 50 & 0 & 1.000 & -0.50 & 0.1758 & 0.0846 & 0.0536 & 0.0940 \\ 
  4 & 50 & -5 & 0.902 & -0.95 & 0.1887 & 0.0896 & 0.0499 & 0.0980 \\ 
  5 & 50 & -5 & 0.902 & -0.75 & 0.1487 & 0.0830 & 0.0522 & 0.0891 \\ 
  6 & 50 & -5 & 0.902 & -0.50 & 0.1081 & 0.0701 & 0.0512 & 0.0811 \\ 
  7 & 50 & -10 & 0.804 & -0.95 & 0.1325 & 0.0894 & 0.0543 & 0.1018 \\ 
  8 & 50 & -10 & 0.804 & -0.75 & 0.1126 & 0.0789 & 0.0462 & 0.0867 \\ 
  9 & 50 & -10 & 0.804 & -0.50 & 0.0887 & 0.0689 & 0.0510 & 0.0820 \\ 
  10 & 50 & -20 & 0.608 & -0.95 & 0.0987 & 0.1266 & 0.0506 & 0.1469 \\ 
  11 & 50 & -20 & 0.608 & -0.75 & 0.0906 & 0.1087 & 0.0506 & 0.1216 \\ 
  12 & 50 & -20 & 0.608 & -0.50 & 0.0682 & 0.0800 & 0.0443 & 0.0948 \\ 
  13 & 50 & -30 & 0.412 & -0.95 & 0.0811 & 0.1666 & 0.0455 & 0.1961 \\ 
  14 & 50 & -30 & 0.412 & -0.75 & 0.0787 & 0.1272 & 0.0500 & 0.1460 \\ 
  15 & 50 & -30 & 0.412 & -0.50 & 0.0719 & 0.1003 & 0.0523 & 0.1195 \\ 
   \hline
\end{tabular}
\end{table}

@@

\caption{Finite-sample rejection rates of the true null for right-tailed  [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with innovations following a CCC-GARCH(1, 1) process (10,000 Monte Carlo samples). }

@@

@@

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process (10,000 Monte Carlo samples). }
\label{tab:cst-garch}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\subsection{A pretest}
\label{pretest}
From equation ... it's easy to see that if $\delta = 0$ the nuisance term $\tau_{c} / \kappa_{c}$ vanishes and the t-statistic collapses to the standard normal  random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. Phillips (1987) shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

@@

To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

\begin{threeparttable}
\begin{tabular}{rrrrrrrr}
 \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4160 & 0.0826 & 0.0483 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2916 & 0.0837 & 0.0515 \\ 
  3 & 50 & -2 & 0.961 & -0.95 & 0.2714 & 0.0868 & 0.0482 \\ 
  4 & 50 & -2 & 0.961 & -0.75 & 0.2079 & 0.0881 & 0.0532 \\ 
  5 & 50 & -20 & 0.608 & -0.95 & 0.0977 & 0.1206 & 0.0515 \\ 
  6 & 50 & -20 & 0.608 & -0.75 & 0.0840 & 0.1078 & 0.0484 \\ 
  7 & 100 & 0 & 1.000 & -0.95 & 0.4217 & 0.0616 & 0.0480 \\ 
  8 & 100 & 0 & 1.000 & -0.75 & 0.2930 & 0.0616 & 0.0497 \\ 
  9 & 100 & -2 & 0.980 & -0.95 & 0.2698 & 0.0587 & 0.0505 \\ 
  10 & 100 & -2 & 0.980 & -0.75 & 0.2104 & 0.0588 & 0.0489 \\ 
  11 & 100 & -20 & 0.802 & -0.95 & 0.1063 & 0.0622 & 0.0471 \\ 
  12 & 100 & -20 & 0.802 & -0.75 & 0.0874 & 0.0514 & 0.0500 \\ 
  13 & 250 & 0 & 1.000 & -0.95 & 0.4259 & 0.0476 & 0.0483 \\ 
  14 & 250 & 0 & 1.000 & -0.75 & 0.2970 & 0.0506 & 0.0536 \\ 
  15 & 250 & -2 & 0.992 & -0.95 & 0.2866 & 0.0507 & 0.0481 \\ 
  16 & 250 & -2 & 0.992 & -0.75 & 0.2092 & 0.0466 & 0.0492 \\ 
  17 & 250 & -20 & 0.920 & -0.95 & 0.1080 & 0.0406 & 0.0517 \\ 
  18 & 250 & -20 & 0.920 & -0.75 & 0.0944 & 0.0369 & 0.0501 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rate close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates}
\centering
\label{tab:cy_changed}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

As argued by Phillips (2014), the Q-test as derived in section (3) is asymptotically invalid when the largest autoregressive root of the regressor is not local to unity. In the following I will demonstrate the finite sample behavior as $\rho$ diverges from unity. Again 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. 
\begin{table}[h!]
\caption{Finite-sample rejection rates (non local to unity autoregressive root) }
\label{tab:non-local}
\centering
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.95 & 0.4147 & 0.0946 & 0.0480 & 0.0957 \\ 
  2 & 50 & 0 & 1.000 & -0.75 & 0.2810 & 0.0838 & 0.0475 & 0.0870 \\ 
  3 & 50 & 0 & 1.000 & -0.50 & 0.1758 & 0.0846 & 0.0536 & 0.0940 \\ 
  4 & 50 & -5 & 0.902 & -0.95 & 0.1887 & 0.0896 & 0.0499 & 0.0980 \\ 
  5 & 50 & -5 & 0.902 & -0.75 & 0.1487 & 0.0830 & 0.0522 & 0.0891 \\ 
  6 & 50 & -5 & 0.902 & -0.50 & 0.1081 & 0.0701 & 0.0512 & 0.0811 \\ 
  7 & 50 & -10 & 0.804 & -0.95 & 0.1325 & 0.0894 & 0.0543 & 0.1018 \\ 
  8 & 50 & -10 & 0.804 & -0.75 & 0.1126 & 0.0789 & 0.0462 & 0.0867 \\ 
  9 & 50 & -10 & 0.804 & -0.50 & 0.0887 & 0.0689 & 0.0510 & 0.0820 \\ 
  10 & 50 & -20 & 0.608 & -0.95 & 0.0987 & 0.1266 & 0.0506 & 0.1469 \\ 
  11 & 50 & -20 & 0.608 & -0.75 & 0.0906 & 0.1087 & 0.0506 & 0.1216 \\ 
  12 & 50 & -20 & 0.608 & -0.50 & 0.0682 & 0.0800 & 0.0443 & 0.0948 \\ 
  13 & 50 & -30 & 0.412 & -0.95 & 0.0811 & 0.1666 & 0.0455 & 0.1961 \\ 
  14 & 50 & -30 & 0.412 & -0.75 & 0.0787 & 0.1272 & 0.0500 & 0.1460 \\ 
  15 & 50 & -30 & 0.412 & -0.50 & 0.0719 & 0.1003 & 0.0523 & 0.1195 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with non local to unity autoregressive root. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{Finite-sample rejection rates (CCC-GARCH(1, 1)) }

@@

\begin{threeparttable}

@@

 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed  [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with innovations following a CCC-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend)}
\label{tab:cst-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}
